Datasamling

### 2022-01-13 Data/Data_Henting_Backup.Rmd

```{r}
hld_arb <- hld_arb %>% 
  mutate(
    Totalt = `1106_Haugesund` + `1135_Sauda` + `1145_Bokn` + `1146_Tysvær` + `1149_Karmøy` + `1160_Vindafjord`) %>% 
  select(NACE2007, Kjonn, Alder, ContentsCode, aar, Totalt)
```

>>>>

```{r}
hld_arb <- hld_arb %>% 
  mutate(
    Totalt = `1106_Haugesund` + `1135_Sauda` + `1145_Bokn` + `1146_Tysvær` + `1149_Karmøy` + `1151_Utsira` + `1160_Vindafjord`) %>% 
  select(NACE2007, Kjonn, Alder, ContentsCode, aar, Totalt)
```
